Combinatorics of the geometry of Wilson loop diagrams

### 2019-01-25 General WLD combinatorics.tex

\begin{dfn}\label{def R(W)}
For $W = (\cP, [n])$, $R(W) = \prod_{e=1}^n R_e$, with $R_e$ defined by the propagators ending on it. For any edge $e$ of $W$, order the propagators incident on $e$ as $\{p_1 \ldots p_r\}$, ordered such that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$. Then \bas R_e =  c_{p_1,e+1} \prod_{j= 1}(r-1) \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_s,e}\;.\eas Note that in this notation, if $r = 1$, $R_e = c_{p,e} c_{p,e+1}$.
\end{dfn}

@@

As we take each $\Delta_{I_i}$ to simply be the determinant of a particular submatrix of $C(W)$, the overall sign of each $\Delta_{I_i}$ is well-defined.  However, we will not be interested in these signs as they only contribute an overall sign to $R$ and our main theorem in this section (Theorem~\ref{thm denom}) will simply be to show that $R$ is equal up to a $\mathbb{Q}$-multiple to the denominator of the Wilson loop diagram (see Definition~\ref{def R(W)}).

@@

\begin{prop}\label{prop alg gives rad}
  With notation as in Algorithm~\ref{alg WLD to denom via GN} and working over the field $\mathbb{Q}$ we have the following:
  \begin{enumerate}
    \item Each $\Delta_{I_i}$ is homogeneous, as is each $r_i$.
    \item Each $\Delta_{I_i}$ splits into linear and quadratic factors.  All linear factors of  $\Delta_{I_i}$ are single variables and all irreducible quadratic factors are $2\times 2$ determinants of single variables.
    \item Quadratic factors in $\Delta_{I_i}$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ with $I_i(p)=a$ and $I_i(q)=b$.
    \item $r_i$ divides $\Delta_{I_i}$.
    \item The ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^{n}\Delta_{I_i}$.
  \end{enumerate}
\end{prop}

@@

All that remains is to prove that $\Delta_{I_i}$ has no irreducible factors of degree 3 or more.  Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$. Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$, we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and \note{would it be neater to note at the beginning that removing vertices which do not support any propagator has no effect so we assume there are no redundant vertices, and hence $i \in I_i$ for each $i$?  No, the point is that we can make it so that $i$ is the first index where a propagator of $f$ contributes, not just that it is in $I_i$.} $i$ contributes to $f$.  Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.  Finally, we can suppose that $W$ is minimal in number of propagators with the above occuring.

>>>>

\begin{dfn}\label{def R(W)}
For $W = (\cP, [n])$, $R(W) = \prod_{e=1}^n R_e$, with $R_e$ defined by the propagators ending on it. For any edge $e$ of $W$, order the propagators incident on $e$ as $\{p_1 \ldots p_r\}$, ordered such that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$. Then \bas R_e =  c_{p_1,e+1} \prod_{j= 1}^{r-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_s,e}\;.\eas Note that in this notation, if $r = 1$, $R_e = c_{p,e} c_{p,e+1}$.
\end{dfn}

@@

As we take each $\Delta_{I_i}$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $\Delta_{I_i}$ is well-defined.  The goal is to show that $R$ is equal to the denominator of the Wilson loop diagram as defined in Definition~\ref{def R(W)}.
%  However, we will not be interested in these signs as they only contribute an overall sign to $R$ and our main theorem in this section (Theorem~\ref{thm denom}) will simply be to show that $R$ is equal up to a $\mathbb{Q}$-multiple to the denominator of the Wilson loop diagram (see Definition~\ref{def R(W)}).

@@

\begin{prop}\label{prop alg gives rad}
  With notation as in Algorithm~\ref{alg WLD to denom via GN} we have the following:
  \begin{enumerate}
    \item Each $\Delta_{I_i}$ is homogeneous, as is each $r_i$.
    \item Each $\Delta_{I_i}$ splits into linear and quadratic factors.  All linear factors of  $\Delta_{I_i}$ are single variables and all irreducible quadratic factors are $2\times 2$ determinants of single variables.
    \item Quadratic factors in $\Delta_{I_i}$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ with $I_i(p)=a$ and $I_i(q)=b$.
    \item $r_i$ divides $\Delta_{I_i}$.
    \item The ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^{n}\Delta_{I_i}$.
  \end{enumerate}
\end{prop}

@@

All that remains is to prove that $\Delta_{I_i}$ has no irreducible factors of degree 3 or more.  Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$. Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$, we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
$i$ contributes to $f$.  Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.  Finally, we can suppose that $W$ is minimal in number of propagators with the above occuring.
